### 2024-10-17 time-series-analysis.qmd
20241016 - duplicate identifiers

### Table of Next Season Predictions {#sec-timeSeriesBayesianGeneratePredictions}

@@

### Plot of Individuals' Model-Implied Predictions {#sec-timeSeriesBayesianGeneratePredictions}

#### Quarterbacks {#sec-fantasyPointsIndividualByAgePlotsQB}

@@

#### Running Backs {#sec-fantasyPointsIndividualByAgePlotsRB}

@@

#### Wide Receivers {#sec-fantasyPointsIndividualByAgePlotsWR}

@@

#### Tight Ends {#sec-fantasyPointsIndividualByAgePlotsTE}

>>>>

### Table of Next Season Predictions {#sec-timeSeriesBayesianNextSeasonPredictions}

@@

### Plot of Individuals' Model-Implied Predictions {#sec-timeSeriesBayesianModelImpliedPredictions}

#### Quarterbacks {#sec-fantasyPointsIndividualByAgeTimeSeriesPlotsQB}

@@

#### Running Backs {#sec-fantasyPointsIndividualByAgeTimeSeriesPlotsRB}

@@

#### Wide Receivers {#sec-fantasyPointsIndividualByAgeTimeSeriesPlotsWR}

@@

#### Tight Ends {#sec-fantasyPointsIndividualByAgeTimeSeriesPlotsTE}
